\noindent \mytitle{come back to yourself}

I think the one thing I should learn from Prakriti is this - the way she has something to come back to, her art. Even if she is in a romantic partnership and has her BPD spiraling, she's still a better artist than a random dude she dates. For me, the closest candidates to something like this have been - literature and mathematics. I need to excel at both of them. I really need to throw myself headfirst into it. Remember the time AL said "I have more interesting things to think about than myself" when I tried to talk about how hollow I felt. I can feel him looking down on me, he clearly thinks he's the smarter person of the two of us, say when he said how he feels alone at a mathematical level, to be fair he isn't even some sort of a genius at this stuff, yet this happens. I need to learn more math. I really do. I don't think I can tolerate feeling like this in a relationship, I need to be better at math, and then also at literature, and show that both can be done. That's how I can truly get someone to attribute some weight to my words. Right now, I am no different than a crank. I am disgustingly undereducated.\\

Okay I changed up my clothes and I'm genuinely not trying to be likeable to other people, just trying to feel confident about myself. and holy shit I feel great, this is sorta a win-win, if people don't like me I still feel good because I like myself better this way, if they do fine. this is so trite, but this is stuff I can't even say out loud to myself in my head because it's weird, maybe a journal should serve this purpose, capture things you're too ashamed to say to yourself as recorded observations, imagine this page being burnt, line by line as you enter things here. Everyone except me is immaterial, it's my world and they're living in it. I love gothic architecture, I'm thinking of Lady Caroline Blackwood, I would be far more charmed by someone like her than someone like David Foster Wallace, DFW was such an incredible bore ugh. Anyway, I have a couple of thoughts I should probably put down let's go to notes app. Anyway, now I'm in meet with him and I'm thinking of what he is thinking, but remember you should always come back to yourself. Come back to all the Math you need to learn, all the books you want to read, all the ways you want to be the person who is entertaining to be alone in a room with, because more likely than not you are the person you are going to spend the most alone time with. Fuck everyone else.\\

Frankie by Alexandria Savior is such an excellent song, her voice is so haunting, so is girlie, hopelessly showbiz, she's got friends you havent met they smoke menthol cigarettes. So you're lucky that she is here, I love drinking, aaaaa. talk about hollywood problems she's got em, she's got em, she calls me girlie.
