\noindent \mytitle{still getting the hang of this thing}

So from the time I last wrote, I almost had a breakup with Alexey, we had a serious conversation, he made me laugh a lot. I drank a lot of gin, Aman fucked up with Aarushi, I don't know what to make of him. The selfish part of me just wants to cut him out of my life because I don't care for the drama. Dhruv sent a rather sappy email. Work life is a complete ruin, so I come here to seek some semblance of sanity.

Now, before I examine and resume the stuff from last day's entry, here's some new stuff: I have a theory, that there's something that I've subconsciously found rather appealing in aristocratic people, or "old money" as tiktok would call it. Thinking of all this from Caroline Blackwood's biography, titled "Dangerous Muse", anyway, it's not so much as the beauty, charms or riches that they possess, but the ugliness of some plebian worries that they are not tarnished by. So my theory is, if I even mentally acted like I was someone raised with utmost elitism, had nothing to be embarrassed about in those senses, have enough of a fortune to not worry about work: then I could truly do something extraordinary, in fact maybe that's the only way I could do something extraordinary. Because I'm too fixated on my deep sense of shame that comes with the clash of reality where plebian concerns exist, and my ideal self not being a person who is formed by those dents. So, as far as I can tell, the only way to stop feeling suffocated, is giving in to the delusion, fake it till you make it or something. 

So I should now soon think about the watered down effects of this, one thing that has happened since I met Alexey is, for the first time, whether in writing or in thoughts, I've developed a strange ability to take myself seriously, where I'm acutely aware of my own voice, as if it's this thing that is only possible when you're deeply seen by someone else. I'm really in love with him. 

Anyway, so 